% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage[utf8]{inputenc}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{Tommy Mattsson\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Contact information}\\
\input{contact.tex}
linkedin.com/in/tommymattsson\\
github.com/Taddic\\
}

\address{{\bf Address}\\
  \input{address.tex}\\
}

\begin{resume}

%\section{Objective}
%Auditing/Analysis of Operations

\section{Education}
{\bf M.Sc,  Computer Science,} Uppsala University, Uppsala, Sweden \hfill \textbf{Ongoing} \\
Sino-Swedish Computer Science and Software Engineering, cooperation with Tongji University, Shanghai, China. Includes studying one year in Shanghai \\
Focusing on networking, distributed systems and software engineering.

{\bf M.Sc, Software Engineering,} Tongji University, Shanghai, China \hfill \textbf{Ongoing} \\
Sino-Swedish Computer Science and Software Engineering, cooperation with Uppsala University, Uppsala, Sweden.\\
Focusing on Software engineering and Chinese language.

{\bf B.Sc, Computer Science,} Uppsala University, Uppsala, Sweden \hfill May 2012 \\
General computer science



\section{Experience}
{\bf Master thesis position,} Ericsson, Shanghai, China \hfill 2013-01 -- 2013-07
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Title of the thesis is "Content filtering". I were to design and implement Internet Content Adaptation Protocol (ICAP, RFC 3507) for a load test tool developed by Ericsson.
 \item Feature implemented in Erlang.
 \item Learned about telecommunication architecture, such as: \\
 GPRS, WCDMA, LTE, SGSN, GGSN, 3G, 2G, PGW, SGW, MME
 \end{itemize}

{\bf Teacher assistant,} Uppsala University, Uppsala, Sweden \hfill 2013-06 -- 2013-08\\
{\bf Teacher assistant,} Uppsala University, Uppsala, Sweden \hfill 2012-06 -- 2012-08
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Teacher assistant for a class named "Peer-To-Peer computing".
 \item Improve previous Erlang labs with a better structure and user interface.
 \item Introduce Erlang to the students.
 \item Attend lab sessions and answer e-mails about lab questions.
 \item Grade lab exercises.
 \end{itemize}

{\bf IT-Support,} Uppsala University, Uppsala, Sweden \hfill 2010-10 -- 2012-08
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Help students with IT related issues mainly regarding the UNIX and Windows computer halls at the IT department of the University.
 \item Maintain printers at IT department.
 \item Prepare new hardware and install operating systems and software, including UNIX/Linux, Mac and Windows systems.
 \end{itemize}

{\bf System developer,} Klarna AB, Stockholm, Sweden \hfill 2009-06 -- 2009-10\\
{\bf System developer,} Klarna AB, Stockholm, Sweden \hfill 2008-06 -- 2008-08
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developing features for Klarnas' online invoice system.
 \item Development performed in the programming language Erlang.
 \item Given more advanced features and slightly more responsibilities second summer due to improved skills in programming.
 \end{itemize}

\newpage
\section{Project}
{\bf Sensor search engine,} Uppsala University, Uppsala, Sverige \hfill 2013-09 -- 2014-01
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Performed in the course "Project Computer Science" for my master degree. The goal of the course was to get a feel of what it is like to work in the industry. Our customer was Ericsson and we also had access to an expert at Sics (www.sics.se)
Implementation was done mainly in Erlang and Ruby on Rails
 \item Open source project hosted on github. \\
 https://github.com/projectcs13/sensor-cloud\\
 https://github.com/projectcs13/sensor-cloud-website
 \end{itemize}

\section{Language \\ Skills}
   \begin{tabular}{l p{3in}}
    Swedish: & Native proficiency \\
    English: & Professional working proficiency \\
    French:  & Elementary proficiency \\
    Chinese:  & Elementary proficiency
 \end{tabular}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Programming language Skills}
   \begin{tabular}{l p{3in}}
    Functional Programming: & Erlang, Haskell, Lisp \\
    Imperative programming: & Java, Python, PHP, C, C++ \\
    Web programming: & JavaScript, HTML, CSS, Ruby on Rails \\
    UNIX/Linux: & Bash scripting, Makefile \\
    App development: & Android API \\
    Other: & LaTeX (this resume is created using LaTeX)
 \end{tabular}

\section{Computer software}
\begin{tabular}{l p{3in}}
	IDE: & Eclipse, Netbeans \\
	CVS: & Git, SVN \\
	Webservers: & Apache, YAWS, Mochiweb \\
	Editors: & Emacs \\
	Databases: & Mnesia, Elastic Search, MySQL
\end{tabular}

\section{Other skills}
\begin{tabular}{l p{3in}}
	Project methodology: & Scrum, Agile development
\end{tabular}

\section{Non-profit activities}
{\bf Training assistant,} TianLong Kungfu, Stockholm, Sweden \hfill 2005 -- 2006
\begin{itemize} \itemsep -2pt
\item Start off Kungfu group training sessions with warm up and basic exercises. Lead entire kungfu sessions on occasion.
\item Occasionally lead entire Kungfu sessions for adolescents, teens and adults.
\end{itemize}

{\bf Kitchen Volounteer,} Vässarö scouting camp, Stockholm, Sweden \hfill Summer 2005
\begin{itemize} \itemsep -2pt
\item I was part of one of the two teams who prepared food for all of the volounteers at the Vässarö scouting complex.
\item Prepared food in the large-scale kitchen of the Vässarö complex.
\end{itemize}

{\bf Sailboat instructor,} Vässarö scouting camp, Stockholm, Sweden \hfill Summer 2004
\begin{itemize} \itemsep -2pt
\item Instruct and supervise adolescents, teens and adults in the usage and safety of sailboats and canoes.
\item Accompanied scout troops on sailing excursions as teacher and supervisor.
\end{itemize}

{\bf Board member,} Flemingsbergs scout troop, Stockholm, Sweden \hfill 2004
\begin{itemize} \itemsep -2pt
\item Attend board meetings and look out for the overall interests of the scout troop.
\end{itemize}
{\bf Leader assistant,} Flemingsbergs scout troop, Stockholm, Sweden \hfill 2004
\begin{itemize} \itemsep -2pt
\item Assist the troop leader and look after the adolescents.
\item Plan scout meetings and excursions for the adolescents.
\end{itemize}

\section{References}
Provided on demand.

\end{resume}
\end{document}
