\documentclass[purpleprocv]{procv}
\begin{document}
    \begin{procv-twocolumns}
        % --------------------------------------
        % First column, spans over all pages
        % --------------------------------------
        \profilepic{profilepicture}
        \aboutme{About me}{
            Software developer eager to learn new 
            things! Asking questions in order to 
            learn new things is a given for me!
            Strong experience in Erlang and Elixir, 
            currently expanding expertise in Python and Golang.
            Throughout my career, I have worked extensively 
            with tools such as Git, Jenkins, Docker and Bash
            to name a few. I am committed to writing 
            high-quality, well-tested, and maintainable 
            code that is clear and accessible to other 
            developers.}
        \begin{skills}{Programming}
            \skillrow{Erlang}{4.5}
            \skillrow{Elixir}{3}
            \skillrow{Python}{2.5}
            \skillrow{Docker}{2}
            \skillrow{Jenkins}{2}
            \skillrow{Html/CSS}{3.5}
            \skillrow{Javascript}{2.5}
            \skillrow{Git/SVN}{3.5}
            \skillrow{Bash}{3}
            \skillrow{\LaTeX}{3.5}
        \end{skills}
        \links{Links}{
            \website{taddic.com/}
            \linkedin{linkedin.com/in/tommymattsson}
            \github{github.com/Taddic}
        }
        \begin{skills}{Languages}
            \skillrow{Swedish}{5}
            \skillrow{English}{4.5}
            \skillrow{French}{1}
        \end{skills}
        \references{References}{References available upon request.}
        \begin{personal}{Personal details}
            \detail{Nationality}{Swedish}
            \detail{Day of birth}{15 June 1987}
        \end{personal}
        \hobbies{Hobbies}
        {In my free time, I like doing acroyoga 
        and cheerleading, playing video games and 
        board games, and getting creative with 
        crafts like woodworking and sewing.}
        %
        % --------------------------------------
        % Second colum, spans over all pages
        % --------------------------------------
        \switchcolumn % This needs to be at the top of the second column
        %
        \header{Tommy}{Matsson}{Software Developer}{
            \input{contactinfo.tex}
        }
        \experience{Work Experience}{
          \exprow{Entryfy}{Stockholm, Sweden}{Sep 2025 - Ongoing}{Elixir, Phoenix LiveView}{System Developer}
          {Focused on backend development with Elixir and interactive web interfaces using Phoenix LiveView.
          \\[3pt]
          Entryfy is a surveillance solutions provider offering comprehensive alarm systems and access card management tailored for businesses.}
          \exprow{Erlang Solutions}{Stockholm, Sweden}{Jun 2023 - Feb 2025}{Erlang, Elixir, rebar3, Github-actions}{Software Developer}
          {Software developer working with clients in the BEAM ecosystem, I designed and delivered reliable, 
          high-performance systems with a focus on Erlang. I provided architectural guidance and best practice 
          consulting, while writing production-grade Erlang code tailored to specific business requirements. During this time, 
          I also learned Elixir, demonstrating adaptability and a proactive approach to broadening my technical capabilities. 
          My work with Erlang Solutions, I contributed to projects where scalability, resilience, and system performance were mission-critical.
          \\[3pt]
          Erlang Solutions is a consulting firm renowned for its profound expertise in Erlang and Elixir, 
          dedicated to advancing and supporting the BEAM ecosystem.}
          \exprow{Klarna}{Stockholm, Sweden}{Sep 2021 - May 2023}{Erlang, Docker, Jenkins, Ansible}{Software Developer}
          {Software developer with a strong focus on Erlang/BEAM, I was part of a four-person Scrum team, "Kred Core",
          responsible for maintaining and extending a critical portion of the legacy Erlang monolith known as "Kred." My 
          work involved contributing to core Erlang code, ensuring system stability and scalability. In addition to 
          backend development, I played a key role in DevOps and CI efforts—maintaining Jenkins instances and creating 
          infrastructure automation using Ansible and Docker.
          \\[3pt]
          Klarna provides payment solutions for e-commerce, with one of its most popular services being 
          "Buy now, receive the products, pay later."}
          \exprow{Telia Company}{Uppsala, Sweden}{Feb 2017 - Aug 2021}{Erlang, Docker, Jenkins}{Software Developer}
          {Software developer specializing in Erlang/BEAM, I played a key role in backend development within an 
          eight-member Scrum team, delivering robust and scalable solutions. My deep knowledge of Erlang and the BEAM 
          allowed me to extend and improve the integration with Facebook APIs and to 
          optimize existing systems for performance and maintainability. I also initiated and implemented critical improvements 
          to the build and deployment pipelines, aligning the team with modern DevOps practices. Using Docker, I set up 
          and maintained Jenkins environments to continuously run previously neglected Erlang test suites. Additionally, I 
          provided cross-team support for these CI/CD systems, driving 
          broader adoption and stability across the development organization.
          \\[3pt]
          Telia is a telecommunications company offering internet, mobile, and other digital services. I worked 
          in the division responsible for developing "ACE", a customer service platform that supports features 
          such as phone queues, email handling, social media integration, and more.}
          \exprow{Cisco Systems}{Stockholm, Sweden}{Aug 2014 - Jan 2017}{}{Support Engineer}
          {Within Cisco I held the same role at Tail-f, which was acquired by Cisco. During this time, 
          I continued to apply my expertise as a support engineer.}
          \exprow{Tail-f Systems}{Stockholm, Sweden}{Mar 2014 - Jul 2014}{YANG, XPath, Erlang, C, Python, Bash}{Support Engineer}
          {Member of a technical support team responsible for assisting customers with the company’s software 
          products, ConfD and NCS. My duties involved managing support tickets through an online system and delivering expert 
          technical resolutions to address customer-reported issues.
          \\[3pt]
          Tail-f Systems developed two software products, ConfD and NCS. ConfD is deployed on network equipment to simplify 
          the creation of user interfaces, while NCS is designed to significantly streamline network management.}
          \exprow{Ericsson}{Shanghai, China}{Jan 2013 - Jul 2013}{Emacs, Erlang, Git}{Master thesis position}
          {Completed a Master’s thesis project centered on Content Filtering, implementing the ICAP protocol (IETF RFC 3507) 
          using Erlang/BEAM. The implementation was designed for seamless integration into a load-testing tool developed by 
          Ericsson, demonstrating practical application of Erlang’s and the BEAM’s strengths in building reliable, concurrent 
          network services. The project also involved studying telecommunication architectures including GPRS, WCDMA, 
          LTE, PGW, and MME.
          \\[3pt]
          Ericsson is a leading global provider of telecommunications equipment and services.}
          \exprow{Klarna}{Stockholm, Sweden}{Jun 2009 - Oct 2009\newline Jun 2008 - Aug 2008}{Erlang, SVN, Emacs, Bash}{Software developer}
          {Software developer during university studies, gaining practical experience through two summer internships at Klarna. I learned the
          Erlang language and implemented small yet meaningful features to support ongoing projects, showcasing 
          a strong early commitment to expanding my technical skills and contributing effectively.
          \\[3pt]
          Klarna provides payment solutions for e-commerce, with one of its most popular services being 
          "Buy now, receive the products, pay later."}
        }
        \experience{Education}{
          \exprow{Uppsala University}{Uppsala, Sweden}{Jan 2014}{}{M.Sc, Computer Science}
          {Uppsala University collaborated with Tongji University for a joint Masters degree, 
          with a focus on networking, distributed systems, and software engineering.}
          \exprow{Tongji University}{Shanghai, China}{Jun 2013}{}{M.Sc, Software Engineering}
          {Tongji University collaborated with Uppsala University for a joint Masters deegree, 
          concentrating on software engineering and Chinese language studies.}
          \exprow{Uppsala University}{Uppsala, Sweden}{May 2012}{}{B.Sc, Computer Science}
          {Focused on developing programming skills, designing algorithms, and analyzing their 
          efficiency, among other foundational computer science principles.}
        }
        \experience{Extra-curricular activities}{
          \exprow{Board member}{Jan 2014 - Jan 2019}{www.uppsalagf.se}{}{Uppsala Gymnastics Club}
          {Held responsibility for the club’s IT, actively contributing to board meetings and 
          executing tasks as directed during these sessions.}
          \exprow{Gymnastics instructor}{Jan 2014 - Jan 2019}{www.uppsalagf.se}{}{Uppsala Gymnastics Club}
          {Planned and led gymnastics training sessions for both children and adults. Provided individualized 
          instruction to support gymnasts’ progression based on their specific needs and goals.}
        }
    \end{procv-twocolumns}
\end{document}
