% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage[utf8]{inputenc}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{CV - Tommy Mattsson\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Contact information}\\
  \input{contact.tex}
  linkedin.com/in/tommymattsson\\
  github.com/Taddic\\
}

\address{{\bf Address}\\
  \input{address.tex}\\
}

\begin{resume}

\section{Experience}
{\bf Software Developer,} Erlang Solutions, Stockholm, Sweden \hfill 2023-06 -- 2025-02
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Develop software primarily written in Erlang.
 \item Learned Elixir.
 \end{itemize}

{\bf Software Developer,} Klarna Bank AB, Stockholm, Sweden \hfill 2021-09 -- 2023-05
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Develop software primarily written in Erlang.
 \item Maintain continuous integration processes with Jenkins pipelines and Bitbucket.
 \end{itemize}

{\bf Software Developer,} Telia Company, Uppsala, Sweden \hfill 2017-02 -- 2021-08
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Develop software primarily written in Erlang, and using Riak.
 \item Setup structure for automatic tests in Erlang running on Jenkins.
 \item Contribute to working on a shift towards Dockers/containers.
 \item Maintain Jenkins instances for building and testing code.
 \end{itemize}

{\bf Support Engineer,} Cisco Systems, Stockholm, Sweden \hfill 2014-08 -- 2017-01
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Same postion as Tail-f, the company was aquired by Cisco.
 \end{itemize}

{\bf Support Engineer,} Tail-f Systems, Stockholm, Sweden \hfill 2014-03 -- 2014-07
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Provide technical support for the software ``ConfD'' and ``NCS''.
 \item Working with technologies such as YANG modeling, NETCONF,
   XML, XPath, Erlang, C, Java, Python.
 \end{itemize}

{\bf Master thesis position,} Ericsson, Shanghai, China \hfill 2013-01 -- 2013-07
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Title of the thesis was ``Content filtering''. I implemented a protocol named
   ICAP (IETF RFC 3507) in Erlang for a load test tool
   developed by Ericsson.
 \item Learned about telecommunication architecture, such as: \\
 GPRS, WCDMA, LTE, SGSN, GGSN, 3G, 2G, PGW, SGW, MME.
 \end{itemize}

{\bf System developer,} Klarna AB, Stockholm, Sweden \hfill 2009-06 -- 2009-10\\
{\bf System developer,} Klarna AB, Stockholm, Sweden \hfill 2008-06 -- 2008-08
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developing features in Erlang for Klarnas' online invoice system.
 \item Summer job during university studies.
 \end{itemize}

\section{Education}
{\bf M.Sc,  Computer Science,} Uppsala University, Uppsala, Sweden \hfill January 2014 \\
Cooperation with Tongji University, Shanghai, China. \\
Focus on networking, distributed systems and software engineering.

{\bf M.Sc, Software Engineering,} Tongji University, Shanghai, China \hfill June 2013 \\
Cooperation with Uppsala University, Uppsala, Sweden.\\
Focus on Software engineering and Chinese language.

{\bf B.Sc, Computer Science,} Uppsala University, Uppsala, Sweden \hfill May 2012 \\
General computer science

\newpage
\section{Non-profit activities}

{\bf Board Member,} Uppsala gymnastics club, Uppsala, Sweden \hfill 2014 -- 2019
\begin{itemize} \itemsep -2pt
\item Responsible for IT in the gymnastics club.
\item Participate in board meetings and workj on specific tasks discussed by the board.
\end{itemize}

{\bf Gymnastic instructor,} Uppsala gymnastics club, Uppsala, Sweden \hfill 2014 -- 2019
\begin{itemize} \itemsep -2pt
\item Plan and lead gymnastic training sessions for children, teens and adults.
\item Help gymnasts progress according to their individual needs and personal goals.
\end{itemize}

\section{Language skills}
\begin{itemize} \itemsep -2pt
\item Swedish (native language)
\item English (fluent in text and speech)
\item French (basic knowledge)
\end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Technical skills}
\begin{itemize} \itemsep -2pt
\item Erlang, Python, JavaScript/NodeJS, C/C++, HTML
\item Bash script, Makefile, Docker
\item LaTeX
\item Emacs, IntelliJ
\item Git, SVN, Jenkins
\end{itemize}

\section{Personal interests}
Privately I practice acroyoga, gymnastics/calisthenics. Computer games is a big interest. I dabble
in carpentry/woodworking and I also have certificate for skydiviing.

\section{References}
Provided on demand.

\end{resume}
\end{document}
